---
title: "ABCD measurement paper preliminary analyses & descriptives"
author: "Meriah DeJoseph"
date: "2020 - 2021"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r}
# Set working directory
setwd("~/Box/!ICD/ABCD/ANALYSES/!REVISION") 

```

# About
This script merges behavioral and RS data and generates two main output files:  
- `df`: Dataframe with brain & bx data. Includes scans with >= 375 volumes & rows with missing RS values for a specific network (due to implausible RS values).  
- `df2`: Version of `df` that only includes participants with complete cases.  

Additionally, this file summarizes participant characteristics & covariates for the complete sample (`df2`).

```{r}
out_file_name = 'clean_df.csv'
```


# Setup
## Libraries
```{r libraries, warning=FALSE, echo=TRUE, include=TRUE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(tidyverse)
library(e1071)

library(readr)
library(Hmisc)
library(corrplot)
library(sjstats)
library(ppcor)


# Multi-level modeling 
#library(lme4)
#library(lmerTest)
#library(bbmle)

# Imputation 
#library(mice)
#library(miceadds)
#library(AICcmodavg)

# Libraries not used 
#library(caret)
#library(ridge)
#library(glmnet)
#library(ggpubr)
#library(finalfit)
#library(jtools)
#library(ggstance)
#library(stats)
#library(psych)
# library(glmmTMB)
#library(cowplot)
#library(fBasics)
#library(dagitty)

#library(xtable)
#library(lqmm)
#library(broom)
#library(insight)

# library(ggplot2)
# library(dplyr)
# library(tidyr)

compareNA <- function(v1,v2) {
  same <- (v1 == v2) | (is.na(v1) & is.na(v2))
  same[is.na(same)] <- FALSE
  return(same)
}
```

## Load data  
```{r load_data, warning=FALSE, include=TRUE, cache=TRUE, message=FALSE}
# MNLFA factor scores 
abcd <- read_csv("Data/ABCD_ALL PREDICTORS_9.7.21.csv")

#RS data 
rs <- read.csv("Data/brainBehavDF.csv")
#drop mean motion in this bc I have it below and it's getting duplicated
rs <- rs %>% select(-c(rsfmri_c_ngd_meanmotion))
#add gordon covariates 
brain_cov <- read.csv("Data/ABCD_rscovars.csv")
brain = inner_join(rs, brain_cov, by = "SUBID") 

#Merge the brain outcome data with the predictors 
df = inner_join(abcd, brain, by = "SUBID") #N=9563 - cases with both Brain and BX
```

## Create variables
```{r}
#Average the left and right to create new vars for models
df$conAmy_2h <- ((df$conAmy_lh + df$conAmy_rh)/2)
df$conHipp_2h <- ((df$conHipp_lh + df$conHipp_rh)/2)
df$conAcc_2h <- ((df$conAcc_lh + df$conAcc_rh)/2)

#Get median splits for moderators to plot 
df <- df %>% 
  mutate(
    DepETAmed = ifelse(DepETA>median(DepETA,na.rm=T), 1, 0),
    ThreatETAmed = ifelse(ThreatETA>median(ThreatETA,na.rm=T), 1, 0),
    SocETAmed = ifelse(SocETA>median(SocETA,na.rm=T), 1, 0),
    # Convert to factors 
    DepETAmed = as.factor(DepETAmed),
    ThreatETAmed = as.factor(ThreatETAmed),
    SocETAmed = as.factor(SocETAmed)
  )

#Make dummies for plots
df$INRBELOW1<-na.pass(ifelse(df$INR <= 1, 1, 0))
df$INRBELOW1 <- as.factor(df$INRBELOW1)
df$HSorLESS <- na.pass(ifelse(df$HIGHED <= 12, 1, 0))
df$HSorLESS <- as.factor(df$HSorLESS)
```

# Clean Data

## Remove scans with too few volumes
```{r remove_bad_scans}
# Filter scans with too few volumes (Hagler et al 2019)
df <- df %>%
  mutate(usable = ifelse(rsfmri_c_ngd_ntpoints>=375,1,0))
table(df$usable)

df <- df %>% filter(usable==1) #7970
```

## Remove implausible rsFC values 
```{r removeConWith}
#Remove rsFC with absolute values > than 0.9
flag_implausible <- function(x) {
  y = ifelse(abs(x)>0.9, 1,0)
  return(y)
}

df <- df %>%
  mutate(outconwith = flag_implausible(conWith),
         outdmnWith = flag_implausible(dmnWith),
         outdanWith = flag_implausible(danWith),
         outvanWith = flag_implausible(vanWith),
         outfparWith = flag_implausible(fparWith),
         outSalWith = flag_implausible(salWith),
         outdmnSal = flag_implausible(dmnSal),
         outdanVan = flag_implausible(danVan),
         outconAmy_2h = flag_implausible(conAmy_2h),
         outconHipp_2h = flag_implausible(conHipp_2h),
         outconAcc_2h = flag_implausible(conAcc_2h))

```

```{r}
table(df$outconwith) 
table(df$outdmnWith) 
table(df$outdanWith) 
table(df$outvanWith) 
table(df$outfparWith) 
table(df$outSalWith) 
table(df$outdmnSal) 
table(df$outdanVan) 
table(df$outconAmy_2h) 
table(df$outconHipp_2h) 
table(df$outconAcc_2h) 
```

```{r}
# Set cases with implausible values to NA
df = df %>%
  mutate(conWith = ifelse(compareNA(outconwith, 1)==1, NA, conWith), 
         dmnWith = ifelse(compareNA(outdmnWith, 1)==1, NA, dmnWith),
         danWith = ifelse(compareNA(outdanWith, 1)==1, NA, danWith),
         vanWith = ifelse(compareNA(outvanWith, 1)==1, NA, vanWith),
         fparWith = ifelse(compareNA(outfparWith, 1)==1, NA, fparWith),
         salWith = ifelse(compareNA(outSalWith, 1)==1, NA, salWith),
         dmnSal = ifelse(compareNA(outdmnSal, 1)==1, NA, dmnSal),
         danVan = ifelse(compareNA(outdanVan, 1)==1, NA, danVan), 
         conAmy_2h = ifelse(compareNA(outconAmy_2h, 1)==1, NA, conAmy_2h),
         conHipp_2h = ifelse(compareNA(outconHipp_2h, 1)==1, NA, conHipp_2h),
         conAcc_2h = ifelse(compareNA(outconAcc_2h, 1)==1, NA, conAcc_2h))
```

```{r}
summary(df$conWith)
summary(df$dmnWith)
summary(df$danWith)
summary(df$vanWith)
summary(df$salWith)
summary(df$dmnSal)
summary(df$danVan)
summary(df$conAmy_2h)
summary(df$conHipp_2h)
summary(df$conAcc_2h)
```

# Participant characteristics
List of participants with complete data
```{r}
df2 = subset(df, 
      !is.na(df$conWith) & 
      !is.na(df$dmnWith) &
      !is.na(df$danWith) &
      !is.na(df$vanWith) &
      !is.na(df$fparWith) &
      !is.na(df$salWith) &
      !is.na(df$salDmn) &
      !is.na(df$danVan) &
      !is.na(df$conAmy_2h) &
      !is.na(df$conHipp_2h) &
      !is.na(df$conAcc_2h))
```

Number of datapoints after keeping complete cases
```{r}
nrow(df2) #7834
```

## Save clean data
```{r}
write.csv(df2, paste(getwd(), out_file_name, sep='/'))
```

```{r}
# Site 
table(df2$sitenum) #reminder: 2 sites gone bc of Phillips
round(prop.table(table(df2$sitenum)), 3)

table(df2$RACE4L)
round(prop.table(table(df2$RACE4L)),3)

table(df2$FEMALE) #1=female
round(prop.table(table(df2$FEMALE)),3)

summary(df2$agemo)
sd(df2$agemo)

summary(df2$INR)
sd(df2$INR, na.rm=T)

summary(df2$HIGHED)
sd(df2$HIGHED, na.rm=T)
```

```{r}
#Compare against full sample -- very similar to analytic sample

table(abcd$sitenum) #reminder: 2 sites gone bc of Phillips
round(prop.table(table(abcd$sitenum)), 3)

table(abcd$RACE4L)
round(prop.table(table(abcd$RACE4L)),3)

table(abcd$FEMALE) #1=female
round(prop.table(table(abcd$FEMALE)), 3)

summary(abcd$agemo)
sd(abcd$agemo)

summary(abcd$INR)
sd(abcd$INR, na.rm=T)

summary(abcd$HIGHED)
sd(abcd$HIGHED, na.rm=T)
```


# Distributions of the predictors
```{r age_distribution, warning=FALSE, message=FALSE, echo=FALSE, include=TRUE, cache=TRUE}
ggplot(data = df2, aes(x = agemo)) + 
  geom_histogram(color = 'black')  +
  labs(x='Age in months')
```

```{r highed_distribution, message=FALSE,warning=FALSE, echo=FALSE, include=TRUE, cache=TRUE}
ggplot(data = df2, aes(x = HIGHED)) + 
  geom_histogram(color = 'black', bins =15) +
  labs(x='Highest education')
```

```{r INR_dist,message=FALSE, warning=FALSE, echo=FALSE, include=TRUE, cache=TRUE}
INRD <- df2 %>% 
  summarise(Mean = mean(INR, na.rm=TRUE),
            SD = sd(INR, na.rm=TRUE),
            Skew= skewness(INR, na.rm=TRUE),
            Kurtosis = kurtosis(INR, na.rm=TRUE))
INRD

ggplot(data=df2, aes(x= INR)) +
  geom_histogram(color = 'black')
```

```{r DEPETA_dist, message=FALSE,warning=FALSE, echo=FALSE, include=TRUE, cache=TRUE}
#Material/econonomic deprivation
DepETAD <- df2 %>% 
  summarise(Mean = mean(DepETA, na.rm=TRUE),
            SD = sd(DepETA, na.rm=TRUE),
            Skew= skewness(DepETA, na.rm=TRUE),
            Kurtosis = kurtosis(DepETA, na.rm=TRUE)
            )
DepETAD

ggplot(data=df2, aes(x= DepETA)) +
  geom_histogram(color = 'black')
```

```{r THREATETA_dist, message=FALSE,warning=FALSE, echo=FALSE, include=TRUE, cache=TRUE}
#Threat
ThreatETAD <- df2 %>% 
  summarise(Mean = mean(ThreatETA, na.rm=TRUE),
            SD = sd(ThreatETA, na.rm=TRUE),
            Skew= skewness(ThreatETA, na.rm=TRUE),
            Kurtosis = kurtosis(ThreatETA, na.rm=TRUE)
            )
ThreatETAD

ggplot(data=df2, aes(x= ThreatETA)) +
  geom_histogram(color = 'black', bins = 50)


```


```{r SOCETA_dist,message=FALSE, warning=FALSE, echo=FALSE, include=TRUE, cache=TRUE}
#Social support
SocETAD <- df2 %>% 
  summarise(Mean = mean(SocETA, na.rm=TRUE),
            SD = sd(SocETA, na.rm=TRUE),
            Skew= skewness(SocETA, na.rm=TRUE),
            Kurtosis = kurtosis(SocETA, na.rm=TRUE)
            )
SocETAD

ggplot(data=df2, aes(x= SocETA)) +
  geom_histogram(color = 'black', bins = 50)
```


# Distributions of the outcomes

## Within-network
```{r conWith_dist, echo=FALSE, include=TRUE, cache=TRUE}
#Cingulo-opercular = con
conWithD <- df2 %>% 
  summarise(Mean = mean(conWith, na.rm=TRUE),
            SD = sd(conWith, na.rm=TRUE),
            Skew= skewness(conWith, na.rm=TRUE),
            Kurtosis = kurtosis(conWith, na.rm=TRUE),
            max = max(conWith, na.rm=TRUE)
            )
conWithD

ggplot(data=df2, aes(x= conWith)) +
  geom_histogram(color = 'black', bins = 50)
```

```{r dmnWith_dist, echo=FALSE, include=TRUE, cache=TRUE}
#Default mode = dmn
dmnWithD <- df2 %>% 
  summarise(Mean = mean(dmnWith, na.rm=TRUE),
            SD = sd(dmnWith, na.rm=TRUE),
            Skew= skewness(dmnWith, na.rm=TRUE),
            Kurtosis = kurtosis(dmnWith, na.rm=TRUE)
            )
dmnWithD

ggplot(data=df2, aes(x= dmnWith)) +
  geom_histogram(color = 'black')
```

```{r danWith_dist, echo=FALSE, include=TRUE, cache=TRUE}
#Dorsal attention = dan
danWithD <- df2 %>% 
  summarise(Mean = mean(danWith, na.rm=TRUE),
            SD = sd(danWith, na.rm=TRUE),
            Skew= skewness(danWith, na.rm=TRUE),
            Kurtosis = kurtosis(danWith, na.rm=TRUE)
            )
danWithD

ggplot(data=df2, aes(x= danWith)) +
  geom_histogram(color = 'black')

```

```{r fparWith_dist, echo=FALSE, include=TRUE, cache=TRUE}
#Fronto-parietal = fpar
fparWithD <- df2 %>% 
  summarise(Mean = mean(fparWith, na.rm=TRUE),
            SD = sd(fparWith, na.rm=TRUE),
            Skew= skewness(fparWith, na.rm=TRUE),
            Kurtosis = kurtosis(fparWith, na.rm=TRUE)
            )
fparWithD

ggplot(data=df2, aes(x= fparWith)) +
  geom_histogram(color = 'black')
```

```{r salWithDist, echo=FALSE, include=TRUE, cache=TRUE}
#Salience = sal
salWithD <- df2 %>% 
  summarise(Mean = mean(salWith, na.rm=TRUE),
            SD = sd(salWith, na.rm=TRUE),
            Skew= skewness(salWith, na.rm=TRUE),
            Kurtosis = kurtosis(salWith, na.rm=TRUE)
            )
salWithD

ggplot(data=df2, aes(x= salWith)) +
  geom_histogram(color = 'black')

```

```{r vanWithDist, echo=FALSE, include=TRUE, cache=TRUE}
#Ventral attention = van
vanWithD <- df2 %>% 
  summarise(Mean = mean(vanWith, na.rm=TRUE),
            SD = sd(vanWith, na.rm=TRUE),
            Skew= skewness(vanWith, na.rm=TRUE),
            Kurtosis = kurtosis(vanWith, na.rm=TRUE)
            )
vanWithD

ggplot(data=df2, aes(x= vanWith)) +
  geom_histogram(color = 'black')
```

## Between-network
```{r salDMN_dist, echo=FALSE, include=TRUE, cache=TRUE}
#Salience and DMN: salDmn
salDmnD <- df2 %>% 
  summarise(Mean = mean(salDmn, na.rm=TRUE),
            SD = sd(salDmn, na.rm=TRUE),
            Skew= skewness(salDmn, na.rm=TRUE),
            Kurtosis = kurtosis(salDmn, na.rm=TRUE)
            )
salDmnD

ggplot(data=df2, aes(x= salDmn)) +
  geom_histogram(color = 'black')
```

```{r danvan_dist, warning=FALSE, echo=FALSE, include=TRUE, cache=TRUE}
#Dorsal attn and ventral attn: danVan
danVanD <- df2 %>% 
  summarise(Mean = mean(danVan, na.rm=TRUE),
            SD = sd(danVan, na.rm=TRUE),
            Skew= skewness(danVan, na.rm=TRUE),
            Kurtosis = kurtosis(danVan, na.rm=TRUE)
            )
danVanD

ggplot(data=df2, aes(x= danVan)) +
  geom_histogram(color = 'black')
```

## Network-ROI
```{r conAmy, warning=FALSE, echo=FALSE, include=TRUE, cache=TRUE}
#cingulo-opercular network connectivity with the amygdala: conAmy_2h
conAmy_2hD <- df2 %>% 
  summarise(Mean = mean(conAmy_2h, na.rm=TRUE),
            SD = sd(conAmy_2h, na.rm=TRUE),
            Skew= skewness(conAmy_2h, na.rm=TRUE),
            Kurtosis = kurtosis(conAmy_2h, na.rm=TRUE)
            )
conAmy_2hD

ggplot(data=df2, aes(x= conAmy_2h)) +
  geom_histogram(color = 'black')
```

```{r conHipp_dist, warning=FALSE, echo=FALSE, include=TRUE, cache=TRUE}
conHipp_2hD <- df2 %>% 
  summarise(Mean = mean(conHipp_2h, na.rm=TRUE),
            SD = sd(conHipp_2h, na.rm=TRUE),
            Skew= skewness(conHipp_2h, na.rm=TRUE),
            Kurtosis = kurtosis(conHipp_2h, na.rm=TRUE)
            )
conHipp_2hD

ggplot(data=df2, aes(x= conHipp_2h)) +
  geom_histogram(color = 'black')
```

```{r conACC_dist, warning=FALSE, echo=FALSE, include=TRUE, cache=TRUE}
#cingulo-opercular network connectivity with the nucleus accumbens: conAcc_2h
conAcc_2hD <- df2 %>% 
  summarise(Mean = mean(conAcc_2h, na.rm=TRUE),
            SD = sd(conAcc_2h, na.rm=TRUE),
            Skew= skewness(conAcc_2h, na.rm=TRUE),
            Kurtosis = kurtosis(conAcc_2h, na.rm=TRUE)
            )
conAcc_2hD

ggplot(data=df2, aes(x= conAcc_2h)) +
  geom_histogram(color = 'black')

```

```{r}
knit_exit()
```


### Density plots as a function of income and education
```{r, warning=FALSE, echo=FALSE, include=TRUE, cache=TRUE}
#########################################
##Density plots highlighting overlap
#########################################

# Look at some descriptives
table(df2$INRBELOW1)
#   0    1 
#6154  954 
table(df2$HSorLESS)
#   0    1 
#7724  104 

# Change outline and fill colors by groups INR at or below 1 = 1
# Use a custom palette
library(ggpubr)

Depdens <-ggdensity(df2, x = "DepETA", 
          add = "mean", rug = TRUE,
          color = "INRBELOW1", fill = "INRBELOW1", 
          xlab="Material & economic deprivation", 
          palette = c("#0073C2FF", "#FC4E07"))

#Depdens <- Depdens + theme(legend.position = "none")
ggsave("Depdens.png", width = 4, height = 4)

Socdens <- ggdensity(df2, x = "SocETA",
          add = "mean", rug = TRUE,
          color = "INRBELOW1", fill = "INRBELOW1", 
          xlab="Caregiver social support", 
          palette = c("#0073C2FF", "#FC4E07"))

#Socdens <- Socdens + theme(legend.position = "none")
ggsave("Socdens.png", width = 4, height = 4)

Threatdens <- ggdensity(df2, x = "ThreatETA",
          add = "mean", rug = TRUE,
          color = "INRBELOW1", fill = "INRBELOW1", 
          xlab="Psychosocial threat", 
          palette = c("#0073C2FF", "#FC4E07"))

#Threatdens <- Threatdens + theme(legend.position = "none")
ggsave("Threatdens.png", width = 4, height = 4)

#Explore whether big diff w/income and education
Edudens <- ggdensity(df2, x = "HIGHED",
          add = "mean", rug = TRUE,
          color = "INRBELOW1", fill = "INRBELOW1", 
          xlab="Years of education", 
          palette = c("#0073C2FF", "#FC4E07"))

#Threatdens <- Threatdens + theme(legend.position = "none")
ggsave("Edudens.png", width = 4, height = 4)


###Education

DepdensED <-ggdensity(df2, x = "DepETA", 
          add = "mean", rug = TRUE,
          color = "HSorLESS", fill = "HSorLESS", 
          xlab="Material & economic deprivation", 
          palette = c("#0073C2FF", "#FC4E07"))

#Depdens <- Depdens + theme(legend.position = "none")
ggsave("DepdensED.png", width = 4, height = 4)

SocdensED <- ggdensity(df2, x = "SocETA",
          add = "mean", rug = TRUE,
          color = "HSorLESS", fill = "HSorLESS", 
          xlab="Caregiver social support", 
          palette = c("#0073C2FF", "#FC4E07"))

#Socdens <- Socdens + theme(legend.position = "none")
ggsave("SocdensED.png", width = 4, height = 4)

ThreatdensED <- ggdensity(df2, x = "ThreatETA",
          add = "mean", rug = TRUE,
          color = "HSorLESS", fill = "HSorLESS", 
          xlab="Psychosocial threat", 
          palette = c("#0073C2FF", "#FC4E07"))

#Threatdens <- Threatdens + theme(legend.position = "none")
ggsave("ThreatdensED.png", width = 4, height = 4)


df2$BLACK = as.factor(df2$BLACK)
df2$HISPANIC = as.factor(df2$HISPANIC)
df2$OTHER = as.factor(df2$OTHER)
df2$WHITE = as.factor(df2$WHITE)

#Explore racial differences in income to examine possible structural influences
INRdensBlack <- ggdensity(df2, x = "INR",
          add = "mean", rug = TRUE,
          color = "BLACK", fill = "BLACK", 
          xlab="INR", 
          palette = c("#0073C2FF", "#FC4E07"))

INRdensHispanic <- ggdensity(df2, x = "INR",
          add = "mean", rug = TRUE,
          color = "HISPANIC", fill = "HISPANIC", 
          xlab="INR", 
          palette = c("#0073C2FF", "#FC4E07"))

INRdensOther <- ggdensity(df2, x = "INR",
          add = "mean", rug = TRUE,
          color = "OTHER", fill = "OTHER", 
          xlab="INR", 
          palette = c("#0073C2FF", "#FC4E07"))

INRdensWhite <- ggdensity(df2, x = "INR",
          add = "mean", rug = TRUE,
          color = "WHITE", fill = "WHITE", 
          xlab="INR", 
          palette = c("#0073C2FF", "#FC4E07"))


```

### Correlations & scatterplots to determine interactions and functional form
```{r, warning=FALSE, echo=FALSE, include=TRUE, cache=TRUE}

library(xtable)
#Make matrix for correlations
my_matrix <- df2[, c("INR", "HIGHED", "DepETA", "ThreatETA", "SocETA", 
                    "conWith", "dmnWith", "danWith", "fparWith", "salWith", "vanWith",
                    "salDmn", "danVan", "conAmy_2h", "conHipp_2h", "conAcc_2h")]
my_cor <- cor(my_matrix,use="complete.obs")
upper<-my_cor
upper[upper.tri(my_cor)]<-""
upper<-as.data.frame(upper)
print(xtable(upper), type="html")

#Another way of looking at correlations
corrplot(my_cor, type="upper", order="hclust", tl.col="black", tl.srt=45)
corrplot(my_cor, method = "color")
col = colorRampPalette(c("#BB4444", "#EE9988", "#FFFFFF", "#77AADD", "#4477AA"))
corrplot(my_cor, method="shade", shade.col=NA, tl.col="black",
                          tl.srt=45, col=col(200), addCoef.col="black", 
                          cl.pos="n", type = "lower", number.cex=0.65)

#More correlations w/ plots
corrplot2 <- pairs.panels(my_matrix[c("INR", "HIGHED", "DepETA", "ThreatETA", "SocETA", 
                    "conWith", "dmnWith", "danWith", "fparWith", "salWith", "vanWith",
                    "salDmn", "danVan", "conAmy_2h", "conHipp_2h", "conAcc_2h")])

#Now do with subsample to see more clearly
ids <- unique(df2$SUBID)   # This creates a vector of identification numbers in the data
subdata <- subset(df2,
                  SUBID %in% sample(ids,size=100))  

#Examine transformations 
#subdata$INR <- sqrt(subdata$INR)

#Make matrix 2 for correlations on subdata
my_matrixsub <- subdata[, c("INR", "HIGHED", "DepETA", "ThreatETA", "SocETA", 
                    "conWith", "dmnWith", "danWith", "fparWith", "salWith", "vanWith",
                    "salDmn", "danVan", "conAmy_2h", "conHipp_2h", "conAcc_2h")]

my_corsub <- cor(my_matrixsub,use="complete.obs")

corsubplot <- pairs.panels(my_matrixsub[c("INR", "HIGHED", "DepETA", "ThreatETA", "SocETA", 
                    "conWith", "dmnWith", "danWith", "fparWith", "salWith", "vanWith",
                    "salDmn", "danVan", "conAmy_2h", "conHipp_2h", "conAcc_2h")])

############

#As one might expect, INR, education, and DepETA are correlated at around .5.
#That's not insane enough to say they are too colinear to keep in the model
#together, but I think it warrants not doing interactions between them bc that
#would be extrapolation for a low SES low Dep group that doesn't really exist
#Let's look at some scatterplots by INR as example
ggplot(df2, aes(x=DepETA, y=conWith, colour=as.factor(INRBELOW1)))+
  geom_point(alpha=.09) +
  stat_smooth(method=lm)
#Yea all the ppl above 1 are clustered near the low end of dep


#######################
#Partial correlations to account for variance that's baked into MNLFA scores
######################

#dep and threat
my_matrix <- df2[, c("DepETA","ThreatETA","agemo","FEMALE", "BLACK", "HISPANIC", "OTHER", "INR", "HIGHED")]
my_matrix <-na.omit(my_matrix)
pcor.test(my_matrix$DepETA, my_matrix$ThreatETA, my_matrix[,c("agemo","FEMALE", "BLACK", "HISPANIC", "OTHER", "INR", "HIGHED")])
#0.03847519

#dep and soc
my_matrix <- df2[, c("DepETA","SocETA","agemo","FEMALE", "BLACK", "HISPANIC", "OTHER", "INR", "HIGHED")]
my_matrix <-na.omit(my_matrix)
pcor.test(my_matrix$DepETA, my_matrix$SocETA, my_matrix[,c("agemo","FEMALE", "BLACK", "HISPANIC", "OTHER", "INR", "HIGHED")])
#-0.004896123

#dep and INR
my_matrix <- df2[, c("DepETA","agemo","FEMALE", "BLACK", "HISPANIC", "OTHER", "INR", "HIGHED")]
my_matrix <-na.omit(my_matrix)
pcor.test(my_matrix$DepETA, my_matrix$INR, my_matrix[,c("BLACK",  "OTHER", "HIGHED")])
#-0.7134458 

#dep and highed
my_matrix <- df2[, c("DepETA","agemo","FEMALE", "BLACK", "HISPANIC", "OTHER", "INR", "HIGHED")]
my_matrix <-na.omit(my_matrix)
pcor.test(my_matrix$DepETA, my_matrix$HIGHED, my_matrix[,c("BLACK",  "OTHER", "INR")])
#-0.1871886 

###


#threat and soc
my_matrix <- df2[, c("ThreatETA","SocETA","agemo","FEMALE", "BLACK", "HISPANIC", "OTHER", "INR", "HIGHED")]
my_matrix <-na.omit(my_matrix)
pcor.test(my_matrix$ThreatETA, my_matrix$SocETA, my_matrix[,c("agemo","FEMALE", "OTHER", "INR")])
#-0.2631113

#threat and INR
my_matrix <- df2[, c("ThreatETA","agemo","FEMALE", "BLACK", "HISPANIC", "OTHER", "INR", "HIGHED")]
my_matrix <-na.omit(my_matrix)
pcor.test(my_matrix$ThreatETA, my_matrix$INR, my_matrix[,c("agemo","FEMALE")])
#-0.247057

#threat and highed
my_matrix <- df2[, c("ThreatETA","agemo","FEMALE", "BLACK", "HISPANIC", "OTHER", "INR", "HIGHED")]
my_matrix <-na.omit(my_matrix)
pcor.test(my_matrix$ThreatETA, my_matrix$HIGHED, my_matrix[,c("agemo","FEMALE")])
#-0.1191264

##

#soc and INR
my_matrix <- df2[, c("SocETA","agemo","FEMALE", "BLACK", "HISPANIC", "OTHER", "INR", "HIGHED")]
my_matrix <-na.omit(my_matrix)
pcor.test(my_matrix$SocETA, my_matrix$INR, my_matrix[,c("agemo","FEMALE", "OTHER")])
#0.04002234

#soc and highed
my_matrix <- df2[, c("SocETA","agemo","FEMALE", "BLACK", "HISPANIC", "OTHER", "INR", "HIGHED")]
my_matrix <-na.omit(my_matrix)
pcor.test(my_matrix$SocETA, my_matrix$HIGHED, my_matrix[,c("agemo","FEMALE", "OTHER", "INR")])
#-0.0009394053

```

### Scatterplots
```{r, warning=FALSE, echo=FALSE, include=TRUE, cache=TRUE}

#Let's look at some scatterplots to see what kinds of functional forms we should test in mixed models
#"conWith", "dmnWith", "danWith", "fparWith", "salWith", "vanWith",
#"salDmn", "danVan", "conAmy_2h", "conHipp_2h", "conAcc_2h"

#Revision request: show cases of SES and DepETA
ggplot(df2, aes(x=INR, y=DepETA))+
  geom_point(alpha=.04) 

ggplot(df2, aes(x=DepETA, y=INR))+
  geom_jitter(alpha=.04) 

ggplot(df2, aes(x=DepETA, y=HIGHED))+
  geom_jitter(alpha=.04) 



###conWith###

#INR 
ggplot(df2, aes(x=INR, y=conWith))+
  geom_point(alpha=.04) +
  stat_smooth()
#EDU 
ggplot(df2, aes(x=HIGHED, y=conWith))+
  geom_point(alpha=.04) +
  stat_smooth()
#DepETA 
ggplot(df2, aes(x=DepETA, y=conWith))+
  geom_point(alpha=.04) +
  stat_smooth()
#ThreatETA 
ggplot(df2, aes(x=ThreatETA, y=conWith))+
  geom_point(alpha=.04) +
  stat_smooth()
#SocETA
ggplot(df2, aes(x=SocETA, y=conWith))+
  geom_point(alpha=.04) +
  stat_smooth()



###dmnWith###

#INR 
ggplot(df2, aes(x=INR, y=dmnWith))+
  geom_point(alpha=.04) +
  stat_smooth()
#EDU 
ggplot(df2, aes(x=HIGHED, y=dmnWith))+
  geom_point(alpha=.04) +
  stat_smooth()
#DepETA 
ggplot(df2, aes(x=DepETA, y=dmnWith))+
  geom_point(alpha=.04) +
  stat_smooth()
#ThreatETA 
ggplot(df2, aes(x=ThreatETA, y=dmnWith))+
  geom_point(alpha=.04) +
  stat_smooth()
#SocETA
ggplot(df2, aes(x=SocETA, y=dmnWith))+
  geom_point(alpha=.04) +
  stat_smooth()

###danWith###

#INR 
ggplot(df2, aes(x=INR, y=danWith))+
  geom_point(alpha=.04) +
  stat_smooth()
#EDU 
ggplot(df2, aes(x=HIGHED, y=danWith))+
  geom_point(alpha=.04) +
  stat_smooth()
#DepETA 
ggplot(df2, aes(x=DepETA, y=danWith))+
  geom_point(alpha=.04) +
  stat_smooth()
#ThreatETA 
ggplot(df2, aes(x=ThreatETA, y=danWith))+
  geom_point(alpha=.04) +
  stat_smooth()
#SocETA
ggplot(df2, aes(x=SocETA, y=danWith))+
  geom_point(alpha=.04) +
  stat_smooth()


###fparWith###

#INR 
ggplot(df2, aes(x=INR, y=fparWith))+
  geom_point(alpha=.04) +
  stat_smooth()
#EDU 
ggplot(df2, aes(x=HIGHED, y=fparWith))+
  geom_point(alpha=.04) +
  stat_smooth()
#DepETA 
ggplot(df2, aes(x=DepETA, y=fparWith))+
  geom_point(alpha=.04) +
  stat_smooth()
#ThreatETA 
ggplot(df2, aes(x=ThreatETA, y=fparWith))+
  geom_point(alpha=.04) +
  stat_smooth()
#SocETA
ggplot(df2, aes(x=SocETA, y=fparWith))+
  geom_point(alpha=.04) +
  stat_smooth()

###salWith###

#INR 
ggplot(df2, aes(x=INR, y=salWith))+
  geom_point(alpha=.04) +
  stat_smooth()
#EDU 
ggplot(df2, aes(x=HIGHED, y=salWith))+
  geom_point(alpha=.04) +
  stat_smooth()
#DepETA 
ggplot(df2, aes(x=DepETA, y=salWith))+
  geom_point(alpha=.04) +
  stat_smooth()
#ThreatETA 
ggplot(df2, aes(x=ThreatETA, y=salWith))+
  geom_point(alpha=.04) +
  stat_smooth()
#SocETA
ggplot(df2, aes(x=SocETA, y=salWith))+
  geom_point(alpha=.04) +
  stat_smooth()


###vanWith###

#INR 
ggplot(df2, aes(x=INR, y=vanWith))+
  geom_point(alpha=.04) +
  stat_smooth()
#EDU 
ggplot(df2, aes(x=HIGHED, y=vanWith))+
  geom_point(alpha=.04) +
  stat_smooth()
#DepETA 
ggplot(df2, aes(x=DepETA, y=vanWith))+
  geom_point(alpha=.04) +
  stat_smooth()
#ThreatETA 
ggplot(df2, aes(x=ThreatETA, y=vanWith))+
  geom_point(alpha=.04) +
  stat_smooth()
#SocETA
ggplot(df2, aes(x=SocETA, y=vanWith))+
  geom_point(alpha=.04) +
  stat_smooth()


###salDmn###

#INR 
ggplot(df2, aes(x=INR, y=salDmn))+
  geom_point(alpha=.04) +
  stat_smooth()
#EDU 
ggplot(df2, aes(x=HIGHED, y=salDmn))+
  geom_point(alpha=.04) +
  stat_smooth()
#DepETA 
ggplot(df2, aes(x=DepETA, y=salDmn))+
  geom_point(alpha=.04) +
  stat_smooth()
#ThreatETA 
ggplot(df2, aes(x=ThreatETA, y=salDmn))+
  geom_point(alpha=.04) +
  stat_smooth()
#SocETA
ggplot(df2, aes(x=SocETA, y=salDmn))+
  geom_point(alpha=.04) +
  stat_smooth()

###danVan###

#INR 
ggplot(df2, aes(x=INR, y=danVan))+
  geom_point(alpha=.04) +
  stat_smooth()
#EDU 
ggplot(df2, aes(x=HIGHED, y=danVan))+
  geom_point(alpha=.04) +
  stat_smooth()
#DepETA 
ggplot(df2, aes(x=DepETA, y=danVan))+
  geom_point(alpha=.04) +
  stat_smooth()
#ThreatETA 
ggplot(df2, aes(x=ThreatETA, y=danVan))+
  geom_point(alpha=.04) +
  stat_smooth()
#SocETA
ggplot(df2, aes(x=SocETA, y=danVan))+
  geom_point(alpha=.04) +
  stat_smooth()


###conAmy_2h###

#INR 
ggplot(df2, aes(x=INR, y=conAmy_2h))+
  geom_point(alpha=.04) +
  stat_smooth()
#EDU 
ggplot(df2, aes(x=HIGHED, y=conAmy_2h))+
  geom_point(alpha=.04) +
  stat_smooth()
#DepETA 
ggplot(df2, aes(x=DepETA, y=conAmy_2h))+
  geom_point(alpha=.04) +
  stat_smooth()
#ThreatETA 
ggplot(df2, aes(x=ThreatETA, y=conAmy_2h))+
  geom_point(alpha=.04) +
  stat_smooth()
#SocETA
ggplot(df2, aes(x=SocETA, y=conAmy_2h))+
  geom_point(alpha=.04) +
  stat_smooth()


###conHipp_2h###

#INR 
ggplot(df2, aes(x=INR, y=conHipp_2h))+
  geom_point(alpha=.04) +
  stat_smooth()
#EDU 
ggplot(df2, aes(x=HIGHED, y=conHipp_2h))+
  geom_point(alpha=.04) +
  stat_smooth()
#DepETA 
ggplot(df2, aes(x=DepETA, y=conHipp_2h))+
  geom_point(alpha=.04) +
  stat_smooth()
#ThreatETA 
ggplot(df2, aes(x=ThreatETA, y=conHipp_2h))+
  geom_point(alpha=.04) +
  stat_smooth()
#SocETA
ggplot(df2, aes(x=SocETA, y=conHipp_2h))+
  geom_point(alpha=.04) +
  stat_smooth()

###conAcc_2h###

#INR 
ggplot(df2, aes(x=INR, y=conAcc_2h))+
  geom_point(alpha=.04) +
  stat_smooth()
#EDU 
ggplot(df2, aes(x=HIGHED, y=conAcc_2h))+
  geom_point(alpha=.04) +
  stat_smooth()
#DepETA 
ggplot(df2, aes(x=DepETA, y=conAcc_2h))+
  geom_point(alpha=.04) +
  stat_smooth()
#ThreatETA 
ggplot(df2, aes(x=ThreatETA, y=conAcc_2h))+
  geom_point(alpha=.04) +
  stat_smooth()
#SocETA
ggplot(df2, aes(x=SocETA, y=conAcc_2h))+
  geom_point(alpha=.04) +
  stat_smooth()

```

### Scatterplots on subsample to double check I can see these functional forms clearly
```{r, warning=FALSE, echo=FALSE, include=TRUE, cache=TRUE}
ids <- unique(df2$SUBID)   # This creates a vector of identification numbers in the data
subdata <- subset(df2,
                  SUBID %in% sample(ids,size=500))  

###conWith###

#INR 
ggplot(subdata, aes(x=INR, y=conWith))+
  geom_point(alpha=.04) +
  stat_smooth()
#EDU 
ggplot(subdata, aes(x=HIGHED, y=conWith))+
  geom_point(alpha=.04) +
  stat_smooth()
#DepETA 
ggplot(subdata, aes(x=DepETA, y=conWith))+
  geom_point(alpha=.04) +
  stat_smooth()
#ThreatETA 
ggplot(subdata, aes(x=ThreatETA, y=conWith))+
  geom_point(alpha=.04) +
  stat_smooth()
#SocETA
ggplot(subdata, aes(x=SocETA, y=conWith))+
  geom_point(alpha=.04) +
  stat_smooth()



###dmnWith###

#INR 
ggplot(subdata, aes(x=INR, y=dmnWith))+
  geom_point(alpha=.04) +
  stat_smooth()
#EDU 
ggplot(subdata, aes(x=HIGHED, y=dmnWith))+
  geom_point(alpha=.04) +
  stat_smooth()
#DepETA 
ggplot(subdata, aes(x=DepETA, y=dmnWith))+
  geom_point(alpha=.04) +
  stat_smooth()
#ThreatETA 
ggplot(subdata, aes(x=ThreatETA, y=dmnWith))+
  geom_point(alpha=.04) +
  stat_smooth()
#SocETA
ggplot(subdata, aes(x=SocETA, y=dmnWith))+
  geom_point(alpha=.04) +
  stat_smooth()

###danWith###

#INR 
ggplot(subdata, aes(x=INR, y=danWith))+
  geom_point(alpha=.04) +
  stat_smooth()
#EDU 
ggplot(subdata, aes(x=HIGHED, y=danWith))+
  geom_point(alpha=.04) +
  stat_smooth()
#DepETA 
ggplot(subdata, aes(x=DepETA, y=danWith))+
  geom_point(alpha=.04) +
  stat_smooth()
#ThreatETA 
ggplot(subdata, aes(x=ThreatETA, y=danWith))+
  geom_point(alpha=.04) +
  stat_smooth()
#SocETA
ggplot(subdata, aes(x=SocETA, y=danWith))+
  geom_point(alpha=.04) +
  stat_smooth()


###fparWith###

#INR 
ggplot(subdata, aes(x=INR, y=fparWith))+
  geom_point(alpha=.04) +
  stat_smooth()
#EDU 
ggplot(subdata, aes(x=HIGHED, y=fparWith))+
  geom_point(alpha=.04) +
  stat_smooth()
#DepETA 
ggplot(subdata, aes(x=DepETA, y=fparWith))+
  geom_point(alpha=.04) +
  stat_smooth()
#ThreatETA 
ggplot(subdata, aes(x=ThreatETA, y=fparWith))+
  geom_point(alpha=.04) +
  stat_smooth()
#SocETA
ggplot(subdata, aes(x=SocETA, y=fparWith))+
  geom_point(alpha=.04) +
  stat_smooth()

###salWith###

#INR 
ggplot(subdata, aes(x=INR, y=salWith))+
  geom_point(alpha=.04) +
  stat_smooth()
#EDU 
ggplot(subdata, aes(x=HIGHED, y=salWith))+
  geom_point(alpha=.04) +
  stat_smooth()
#DepETA 
ggplot(subdata, aes(x=DepETA, y=salWith))+
  geom_point(alpha=.04) +
  stat_smooth()
#ThreatETA 
ggplot(subdata, aes(x=ThreatETA, y=salWith))+
  geom_point(alpha=.04) +
  stat_smooth()
#SocETA
ggplot(subdata, aes(x=SocETA, y=salWith))+
  geom_point(alpha=.04) +
  stat_smooth()


###vanWith###

#INR 
ggplot(subdata, aes(x=INR, y=vanWith))+
  geom_point(alpha=.04) +
  stat_smooth()
#EDU 
ggplot(subdata, aes(x=HIGHED, y=vanWith))+
  geom_point(alpha=.04) +
  stat_smooth()
#DepETA 
ggplot(subdata, aes(x=DepETA, y=vanWith))+
  geom_point(alpha=.04) +
  stat_smooth()
#ThreatETA 
ggplot(subdata, aes(x=ThreatETA, y=vanWith))+
  geom_point(alpha=.04) +
  stat_smooth()
#SocETA
ggplot(subdata, aes(x=SocETA, y=vanWith))+
  geom_point(alpha=.04) +
  stat_smooth()


###salDmn###

#INR 
ggplot(subdata, aes(x=INR, y=salDmn))+
  geom_point(alpha=.04) +
  stat_smooth()
#EDU 
ggplot(subdata, aes(x=HIGHED, y=salDmn))+
  geom_point(alpha=.04) +
  stat_smooth()
#DepETA 
ggplot(subdata, aes(x=DepETA, y=salDmn))+
  geom_point(alpha=.04) +
  stat_smooth()
#ThreatETA 
ggplot(subdata, aes(x=ThreatETA, y=salDmn))+
  geom_point(alpha=.04) +
  stat_smooth()
#SocETA
ggplot(subdata, aes(x=SocETA, y=salDmn))+
  geom_point(alpha=.04) +
  stat_smooth()

###danVan###

#INR 
ggplot(subdata, aes(x=INR, y=danVan))+
  geom_point(alpha=.04) +
  stat_smooth()
#EDU 
ggplot(subdata, aes(x=HIGHED, y=danVan))+
  geom_point(alpha=.04) +
  stat_smooth()
#DepETA 
ggplot(subdata, aes(x=DepETA, y=danVan))+
  geom_point(alpha=.04) +
  stat_smooth()
#ThreatETA 
ggplot(subdata, aes(x=ThreatETA, y=danVan))+
  geom_point(alpha=.04) +
  stat_smooth()
#SocETA
ggplot(subdata, aes(x=SocETA, y=danVan))+
  geom_point(alpha=.04) +
  stat_smooth()


###conAmy_2h###

#INR 
ggplot(subdata, aes(x=INR, y=conAmy_2h))+
  geom_point(alpha=.04) +
  stat_smooth()
#EDU 
ggplot(subdata, aes(x=HIGHED, y=conAmy_2h))+
  geom_point(alpha=.04) +
  stat_smooth()
#DepETA 
ggplot(subdata, aes(x=DepETA, y=conAmy_2h))+
  geom_point(alpha=.04) +
  stat_smooth()
#ThreatETA 
ggplot(subdata, aes(x=ThreatETA, y=conAmy_2h))+
  geom_point(alpha=.04) +
  stat_smooth()
#SocETA
ggplot(subdata, aes(x=SocETA, y=conAmy_2h))+
  geom_point(alpha=.04) +
  stat_smooth()


###conHipp_2h###

#INR 
ggplot(subdata, aes(x=INR, y=conHipp_2h))+
  geom_point(alpha=.04) +
  stat_smooth()
#EDU 
ggplot(subdata, aes(x=HIGHED, y=conHipp_2h))+
  geom_point(alpha=.04) +
  stat_smooth()
#DepETA 
ggplot(subdata, aes(x=DepETA, y=conHipp_2h))+
  geom_point(alpha=.04) +
  stat_smooth()
#ThreatETA 
ggplot(subdata, aes(x=ThreatETA, y=conHipp_2h))+
  geom_point(alpha=.04) +
  stat_smooth()
#SocETA
ggplot(subdata, aes(x=SocETA, y=conHipp_2h))+
  geom_point(alpha=.04) +
  stat_smooth()

###conAcc_2h###

#INR 
ggplot(subdata, aes(x=INR, y=conAcc_2h))+
  geom_point(alpha=.04) +
  stat_smooth()
#EDU 
ggplot(subdata, aes(x=HIGHED, y=conAcc_2h))+
  geom_point(alpha=.04) +
  stat_smooth()
#DepETA 
ggplot(subdata, aes(x=DepETA, y=conAcc_2h))+
  geom_point(alpha=.04) +
  stat_smooth()
#ThreatETA 
ggplot(subdata, aes(x=ThreatETA, y=conAcc_2h))+
  geom_point(alpha=.04) +
  stat_smooth()
#SocETA
ggplot(subdata, aes(x=SocETA, y=conAcc_2h))+
  geom_point(alpha=.04) +
  stat_smooth()
```
